Paper_analyses

### 2021-07-23 Paper_Analyses_subj_obje_arousal.Rmd
#1 fixed the code
the code is now working without warning, but need to split for each estimate

Pupil velocity test

velocity analyses
```{r}
# thought maybe it has soemthing to to with the velcity, velocity is sidderent

@@

100ms
```{r}
unique(tmp.df4_full_stim_downs_jun2021_60bins$ssid)

@@

>>>>

Pupil velocity test
# velocity analyses

```{r}
# thought maybe it has soemthing to to with the velcity, velocity is sidderent

@@

velocity 100ms
```{r}
unique(tmp.df4_full_stim_downs_jun2021_60bins$ssid)

@@

velocity timecourse
```{r}
# let's test the interaction term
nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)

# create and empty dataframe for the timecourse analyses
timecourse_60bin_result_df_vel <- data.frame(timebins= rep(NA, 60), Estimate= rep(NA, 60), 
                                   t=rep(NA, 60), p=rep(NA, 60), cov= as.character(rep(NA,60)))

# i =1
tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth

tmp.df4_full_stim_downs_jun2021_60bins$pup_vel_smooth

nbins<- nbins[3:56]

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_vel_smooth ~ (arousal_c* valence)+Mean_gray_z  +
                                (1 | ssid),
                                # (0 +arousal_c* valence | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    !is.na(pup_vel_smooth)&
                                    timebin_no == nbins[b]))

        #store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_60bin_result_df_vel[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] #save the exact value of time bin
            timecourse_60bin_result_df_vel[i,2]<-
              lmer_bin_pup_summary[["coefficients"]][5,1] 
            # first number is term(row), second is column
            timecourse_60bin_result_df_vel[i,3]<-
              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
            timecourse_60bin_result_df_vel[i,4]<-
              lmer_bin_pup_summary[["coefficients"]][5,5] # p value
            # simulated_clusters_JEFFE[i,6]<- nsim[s] #store simulation ount
            timecourse_60bin_result_df_vel[i,5] <-
              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

# timecourse_result_df_pos<- timecourse_result_df
View(timecourse_60bin_result_df_vel)

timecourse_60bin_result_df_vel %>%
  ggplot(aes(timebins, t))+
  geom_line(size = 2)+
  geom_line(aes(y = p), linetype = "dashed", size = 2)+
  geom_hline(yintercept = .05, color = 'red', size = 1.5)
